Puck Predictions: Unraveling the NHL Game Forecasting Riddle

### 2024-03-29 Latex/draft.tex
added a few more things to MCMC LaTeX

            \State $\text{event\_time} \gets \text{sample from } \text{KDE\_times()}$
            \State $\text{time\_remaining} \gets (\text{time\_remaining} - \text{event\_time})$
        \EndWhile
    \end{algorithmic}
    \label{alg:monte_carlo_algorithm}
\end{algorithm}
The KDE\_times() is a KDE model fit on the amount of seconds that transpired between each hockey event for all NHL games over the course of 13 years. This KDE model resembled a poisson distribution with $\lambda \approx 18$. During the course of the algorithm, we maintained a count of all of the events that transpired. Upon termination of the simulation, we compared home goals to away goals and termed a winner. If there was a tie, we would run the algorithm until another team scored a goal, thus simulating overtime per NHL rules.

@@

To evaluate our simulation's effectiveness at accurately modeling actual hockey games, we combined a dataset with the final event counts for 1500 actual hockey games and for 1500 simulated games. We then performed PCA, t-SNE and UMAP dimensionality reductions using various perplexity and neighbor hyperparameters to see if these algorithms clustered the synthetic games and actual games in different clusters. As shown below in \ref{fig:simulation_v_actual}

>>>>

            \State $\text{event\_time} \gets \text{sample from } \text{KDE\_times()}$
            \State $\text{time\_remaining} \gets (\text{time\_remaining} - \text{event\_time})$
        \EndWhile
    \end{algorithmic}
    \label{alg:monte_carlo_algorithm}
\end{algorithm}
The KDE\_times() is a KDE model fit on the amount of seconds that transpired between 
each hockey event for all NHL games over the course of 13 years. This KDE model 
resembled a poisson distribution with $\lambda \approx 18$. During the course of 
the algorithm, we maintained a count of all of the events that transpired. Upon 
termination of the simulation, we compared home goals to away goals and termed 
a winner. If there was a tie, we would run the algorithm until another team scored0 
a goal, thus simulating overtime per NHL rules.

@@

To evaluate our simulation's effectiveness at accurately modeling actual hockey 
games, we combined a dataset with the final event counts for 1500 actual hockey 
games and for 1500 simulated games. We then performed PCA, t-SNE and UMAP 
dimensionality reductions using various perplexity and neighbor hyperparameters 
to see if these algorithms clustered the synthetic games and actual games in 
different clusters. As shown below in \ref{fig:simulation_v_actual}, the simulated
games and actual games are all clustered together, thus demonstrating that our
simulation effectively emulates live NHL games.
